Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2017-12-13 pkg/disttree/inst/draft/draft.Rnw
playing around with bg and lwd in Fig 2; new title suggestion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1849 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0320dbc9d9bf15d4efd7c7b2e0a40188917fd6a5

%\VignetteIndexEntry{disttree: Distributional Trees and Forests}
%\VignetteDepends{partykit, gamlss.dist}
%\VignetteKeywords{regression trees, random forests, distributional regression, recursive partitioning}
%\VignettePackage{disttree}

@@

\title{Distributional Trees and Forests}
\Plaintitle{disttree: Distributional Trees and Forests}

@@

<<plot_motivation_distforest, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
points(x, y, col = "slategray", pch = 19)
box(lwd=12)
@
\end{center}
\endminipage};
\node (d) at (0,-2) 
{
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
Regression Tree 
\end{center}
\endminipage};
\node (e) at (5,-2) 
{
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
Random Forest 
\end{center}
\endminipage};
\node at (10,-2)
{
\minipage{0.28\textwidth}
\begin{center}
\vspace{0.0cm}
Distributional Forest 
\end{center}
\endminipage};
\node (g) at (0,-5.4) 
{
\minipage{0.29\textwidth}
\vspace{0.2cm}
%\hspace{0.0cm}
\begin{center}
<<motivation_disttree, echo=FALSE, results=hide>>=
## disttree
set.seed(74)
x <- c(1:nobs)/nobs
var <- ytree/3
y <- ytrue + rnorm(nobs,0,var)
@

<<plot_motivation_disttree, fig=TRUE, echo=FALSE>>=
par(mar=c(2,0,2,0))
plot(x = x, y = y, xaxt="n", yaxt="n", ann=FALSE, col = "slategray", pch = 19)
lines(x = x, y = ytree, col = pal["forest"], lwd=7, main = "")
polygon(c(x, rev(x)), c(ytree + var, rev(ytree - var)),
  col = pallight["forest"], border = "transparent")
box(lwd=12)
@
\vspace{-0.2cm}%\\
Distributional Tree
\vspace{0.2cm}
\end{center}
\endminipage};
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](2.1,0)--(2.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=1.4pt](7.1,0)--(7.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=1.4pt](0,-2.4)--(0,-3.2);
\draw[-{>[scale=4, length=2, width=3]},line width=1.4pt](2.2,-5.4)--(7.9,-2.5);
\end{tikzpicture}
\caption{\label{Devel_treeforest}Development in the field of algorithmic trees and forests: regression tree (top left), distributional tree (bottom), random forest (top middle), distributional forest (top right).}
\end{figure}

>>>>

%\VignetteIndexEntry{disttree: Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain}
%\VignetteDepends{partykit, gamlss.dist}
%\VignetteKeywords{regression trees, random forests, distributional regression, recursive partitioning}
%\VignettePackage{disttree}

@@

\title{Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain}

@@

<<plot_motivation_distforest, fig=TRUE, echo=FALSE>>=
par(mar = c(2, 0, 2, 0))
plot(x, y, xaxt = "n", yaxt = "n", ann = FALSE, type = "n")
usr <- par("usr")
rect(usr[1], usr[3], usr[2], usr[4], col = gray(0.94), border = "transparent")
polygon(c(x, rev(x)), c(ytrue + 0.1 + var, rev(ytrue - 0.1 - var)),
  col = pallight["forest"], border = "transparent")
lines(x = x, y = yforest, col = pal["forest"], lwd=7, main = "")
points(x, y, col = "slategray", pch = 19)
box(lwd=8)
@
\end{center}
\endminipage};
\node (d) at (0,-2) 
{
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
Regression Tree 
\end{center}
\endminipage};
\node (e) at (5,-2) 
{
\minipage{0.29\textwidth}
\begin{center}
\vspace{0.0cm}
Random Forest 
\end{center}
\endminipage};
\node at (10,-2)
{
\minipage{0.28\textwidth}
\begin{center}
\vspace{0.0cm}
Distributional Forest 
\end{center}
\endminipage};
\node (g) at (0,-5.4) 
{
\minipage{0.29\textwidth}
\vspace{0.2cm}
%\hspace{0.0cm}
\begin{center}
<<motivation_disttree, echo=FALSE, results=hide>>=
## disttree
set.seed(74)
x <- c(1:nobs)/nobs
var <- ytree/3
y <- ytrue + rnorm(nobs,0,var)
@

<<plot_motivation_disttree, fig=TRUE, echo=FALSE>>=
par(mar = c(2, 0, 2, 0))
plot(x, y, xaxt="n", yaxt="n", ann=FALSE, type = "n")
usr <- par("usr")
rect(usr[1], usr[3], usr[2], usr[4], col = gray(0.94), border = "transparent")
lines(x = x, y = ytree, col = pal["forest"], lwd=7, main = "")
polygon(c(x, rev(x)), c(ytree + var, rev(ytree - var)),
  col = pallight["forest"], border = "transparent")
points(x, y, col = "slategray", pch = 19)
box(lwd=8)
@
\vspace{-0.2cm}%\\
Distributional Tree
\vspace{0.2cm}
\end{center}
\endminipage};
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](2.1,0)--(2.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](7.1,0)--(7.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](0,-2.4)--(0,-3.2);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](2.2,-5.4)--(7.9,-2.5);
\end{tikzpicture}
\caption{\label{Devel_treeforest}Development in the field of algorithmic trees and forests: regression tree (top left), distributional tree (bottom), random forest (top middle), distributional forest (top right).}
\end{figure}
